\section{Representation in First-Order Logic (FOL)}
\begin{large}
    \textbf{Consider the following baseball vocabulary:}
    \begin{enumerate}
        \item $Pitcher(p)$ \textbf{is a predicate where person} $p$ \textbf{is a pitcher}.
        \item $flies(p_1, p_2)$ \textbf{is a predicate where person} $p_1$ \textbf{flies}\footnote{A flyout occurs when a batter hits the ball in the air, and a fielder catches it before it touches the ground.} \textbf{ out to person }$p_2$.
        \item $Centerfielder(p)$ \textbf{is a predicate where person} $p$ \textbf{is a centerfielder.}
        \item $scores(p)$ \textbf{is a predicate where person} $p$\textbf{ scores.}
        \item $friend(p_1, p_2)$ \textbf{is a predicate where person }$p_1$\textbf{ is the friend of person} $p_2$ \textbf{(but not vice versa).}
        \item \textbf{Robinson, Crabb, Samson, Jones are constants denoting persons.}
    \end{enumerate}
    \textbf{Now look at the following translations of natural language into first order logic statements describing
        a baseball game. Using the provided vocabulary, translate the conclusion of each of the
        following arguments into an FOL statement.}
\end{large}

\subsection{Argument A}
\begin{large}
    \textbf{Only pitchers fly out to Robinson. Crabb scores only if Samson flies out to Robinson and Robinson is a
        centerfielder. Crabb scores.
        Conclusion: Samson is a pitcher.}\
    \begin{itemize}
        \item $\mathbf{\forall x : [flies(x, Robinson) \rightarrow Pitcher(x)]}$
        \item $\mathbf{scores(Crabb) \rightarrow (flies(Samson, Robinson) \land Centerfielder(Robinson))}$
        \item $\mathbf{scores(Crabb)}$
    \end{itemize}

    Translated into FOL we get:

    $\textcolor{PineGreen}{\forall x : (flies(x, Robinson) \rightarrow Pitcher(x))} \\
    \textcolor{PineGreen}{\land (scores(Crabb) \rightarrow (flies(Samson, Robinson) \land Centerfielder(Robinson)))} \\
        \land scores(Crabb) \\
        \textcolor{Plum}{\rightarrow Pitcher(Samson)}$
\end{large}


\subsection{Argument B}
\begin{large}
    \textbf{No centerfielder who does not score has any friends. Robinson and Jones are both centerfielders. Any
        centerfielder who flies out to Jones does not score. Robinson flies out to Jones.
        Conclusion: Jones is not a friend of Robinson.}
    \begin{itemize}
        \item $\mathbf{\forall x : [(Centerfielder(x) \land \neg scores(x)) \rightarrow \neg \exists y : [friend(y, x)]]}$
        \item $\mathbf{Centerfielder(Robinson) \land Centerfielder(Jones)}$
        \item $\mathbf{\forall x : [(Centerfielder(x) \land flies(x, Jones)) \rightarrow \neg scores(x)]}$
        \item $\mathbf{flies(Robinson, Jones)}$
    \end{itemize}
    \textbf{Square brackets [] are used to stress which parts of the statement belong under which quantifier.}

    Translated into FOL we get:

    $\textcolor{PineGreen}{\forall x : ((Centerfielder(x) \land \neg scores(x)) \rightarrow \neg \exists y : [friend(y, x)])} \\
        \textcolor{PineGreen}{\land (Centerfielder(Robinson) \land Centerfielder(Jones))} \\
        \textcolor{PineGreen}{\land [\forall x : [(Centerfielder(x) \land flies(x, Jones)) \rightarrow \neg scores(x)]]}\\
        \land flies(Robinson, Jones) \\
        \textcolor{Plum}{\rightarrow \neg friend(Robinson, Jones)}$
\end{large}